Supplementary Material for Asymmetry paper

### 2020-05-26 Supplementary/Sup_mat.Rmd
Updated sup mat
Still need to run version with latest model

# run model
Hoop_size_m1 <- brm(norm_dist2 ~ norm_hoop_pos + (norm_hoop_pos|participant), 
                    data = model_data,
                    family = "beta",
                    prior = c(set_prior("student_t(3,0,1)", class = "b"),
                              set_prior("student_t(3,0,1)", class = "Intercept")),
                    cores = 1,
                    chains = 1,
                    iter = 5000,
                    warmup = 2500,
                    control = list(adapt_delta = .95, max_treedepth = 15))

@@

## Experiment 2: Two Throws
```{r load in model for two throws, include = F, echo = F}
# load("../Analyses/Experiment_2_Two_throw/modelling/model_outputs/m1_pos")
# load("../Analyses/Experiment_2_Two_throw/modelling/model_outputs/m1_pos_draws")
```

```{r Two-throws modelling, include = F, echo = F, cache = T}
load("../Analyses/Experiment_2_Two_throw/scratch/model_data_pos")

source("extract_draws_functions/Two_throw_draws.R")

Two_throw_m1 <- brm(abspos ~ norm_delta * Num_throws + (norm_delta * Num_throws|Participant),
                    family = "beta",
                    data = model_data_pos,
                    prior = c(set_prior("student_t(3,0,3)", class = "b")),
                    cores = 1,
                    chains = 1,
                    iter = 2000,
                    warmup = 1000)

draws <- draw_post_delta(Two_throw_m1, model_data_pos)

>>>>

# run model
Hoop_size_m1 <- brm(norm_dist2 ~ norm_hoop_pos + (norm_hoop_pos|participant), 
                    data = model_data,
                    family = "beta",
                    prior = c(set_prior("student_t(3, 0, 1)",
                                            coef = "norm_hoop_pos",
                                            class = "b"),
                                  set_prior("student_t(3,0,1)",
                                            class = "Intercept")),
                    cores = 2,
                    chains = 2,
                    iter = 5000,
                    warmup = 2500,
                    control = list(adapt_delta = .95, max_treedepth = 15))

@@

## Experiment 2: Two Throws
```{r Two Throws: load data, include = F, echo = F}
load("../Analyses/Experiment_2_Two_throw/scratch/model_data_pos")

source("extract_draws_functions/Two_throw_draws.R")
```

```{r Two_Throws_Priors_only_model, include = F, echo = F, cache = T}
Two_throw_priors <- brm(abspos ~ norm_delta * Num_throws + (norm_delta * Num_throws|Participant),
                        family = "beta",
                        data = model_data_pos,
                        prior = c(set_prior("student_t(4,0,.8)",
                                            class = "b",
                                            coef = "norm_delta"),
                                  set_prior("student_t(4,0,.8)",
                                            class = "b",
                                            coef = "norm_delta:Num_throwsTwoMThrows"),
                                  set_prior("student_t(4,0,.8)",
                                            class = "b", coef = "Num_throwsTwoMThrows"),
                                  set_prior("student_t(4,0,.8)",
                                            class = "Intercept")),
                        cores = 1,
                        chains = 1,
                        iter = 10000,
                        warmup = 5000,
                        control = list(adapt_delta = .99, max_treedepth = 15),
                        sample_prior = "only")

# test 
close <- min(model_data_pos$norm_delta)
mid <- median(model_data_pos$norm_delta)
far <- max(model_data_pos$norm_delta)

draws_df <- Two_throw_priors  %>% 
  spread_draws(b_Intercept,
               b_norm_delta,
               b_Num_throwsTwoMThrows,
               `b_norm_delta:Num_throwsTwoMThrows`) %>%
  mutate(One_throw = b_Intercept,
         Norm_delta_OT = b_norm_delta,
         Two_throw = b_Num_throwsTwoMThrows,
         Norm_delta_TT = `b_norm_delta:Num_throwsTwoMThrows`) %>% 
  select(-b_Intercept,
         -b_norm_delta,
         -b_Num_throwsTwoMThrows,
         -`b_norm_delta:Num_throwsTwoMThrows`) %>%
  mutate(hoop_Close.One_throw = One_throw + (close * Norm_delta_OT),
         hoop_Mid.One_throw = One_throw + (mid * Norm_delta_OT),
         hoop_Far.One_throw = One_throw + (far * Norm_delta_OT),
         hoop_Close.Two_throw = One_throw + Two_throw + (close * Norm_delta_TT),
         hoop_Mid.Two_throw = One_throw + Two_throw + (mid * Norm_delta_TT),
         hoop_Far.Two_throw = One_throw + Two_throw + (far * Norm_delta_TT)) %>%
  select(.iteration,
         hoop_Close.One_throw,
         hoop_Mid.One_throw,
         hoop_Far.One_throw,
         hoop_Close.Two_throw,
         hoop_Mid.Two_throw,
         hoop_Far.Two_throw) %>% 
  gather(c(hoop_Close.One_throw:hoop_Far.Two_throw),
         key = "parameter",
         value = "estimate") %>% 
  separate(parameter,
           into= c("Dist_type", "Num_throws"),
           sep = "\\.") %>% 
  separate(Dist_type, 
           into = c("remove", "Dist_type"),
           sep = "_") %>% 
  select(-remove)

priors_plt <- draws_df %>% 
  mutate(prop = boot::inv.logit(estimate)) %>% 
  ggplot(aes(prop, 
             colour = Num_throws,
             fill = Num_throws)) + 
  geom_density(
    kernel = "biweight",
    alpha = .3
    )+ 
  facet_wrap(~Dist_type) + 
  theme_bw()
```

```{r PltTwoThrowPriors, include = T, echo = F, fig.asp=.45, fig.cap="_Posterior for the priors only model_"}
priors_plt
```

```{r Two-throws modelling, include = F, echo = F, cache = T}
# Two_throw_m1 <- brm(abspos ~ norm_delta * Num_throws + (norm_delta * Num_throws|Participant),
#                     family = "beta",
#                     data = model_data_pos,
#                     prior = c(set_prior("student_t(4,0,.8)",
#                                             class = "b",
#                                             coef = "norm_delta"),
#                                   set_prior("student_t(4,0,.8)",
#                                             class = "b",
#                                             coef = "norm_delta:Num_throwsTwoMThrows"),
#                                   set_prior("student_t(4,0,.8)",
#                                             class = "b", coef = "Num_throwsTwoMThrows"),
#                                   set_prior("student_t(4,0,.8)",
#                                             class = "Intercept")),
#                         cores = 1,
#                         chains = 1,
#                         iter = 6500,
#                         warmup = 3250,
#                         control = list(adapt_delta = .99, max_treedepth = 15))

load("../Analyses/Experiment_2_Two_throw/modelling/model_outputs/m1_pos")
draws <- draw_post_delta(m1_pos, model_data_pos)
